\documentclass[a5paper,twoside]{article}
\usepackage[T1]{fontenc}
\usepackage[]{geometry}
\usepackage[parfill]{parskip}
\usepackage{libertine}
\usepackage[autocompile]{gregoriotex}
\usepackage[center]{titlesec}

\input{variables}

\begin{document}
\section*{The Introductory Rites}

\emph{The Introit chant or an appropriate hymn is sung as the ministers and servers process into the santuary. All stand.}

\priest\sign

\all{\textbf{Amen.}}

\priest\greeting

\all{\textbf{And with your spirit.}}

\priest\penitentialintro

\all\confiteor

\priest\absolution

\all{\textbf{Amen.}}

\all\emph{The priest/cantor sings each invocation, and the congregation respond by repetition, or by written out response.}

\kyrie

\priest\oremus

\emph{The priest sings or says the collect, to which all respond:}

\all{\textbf{Amen.}}

\section*{The Liturgy of the Word}

\emph{All sit for the readings}

\subsection*{First Reading}

\emph{After the first reading}

\reader\verbumdomini

\all{\textbf{Thanks be to God.}}

\emph{The Gradual or Responsorial Psalm is sung.}

\subsection*{Second Reading}

\emph{After the second reading}

\reader\verbumdomini

\all{\textbf{Thanks be to God.}}

\emph{The Alleluia, Tract or Gospel Acclamation is sung, at which point all stand.}

\subsection*{Gospel}

\deacon\greeting

\all{\textbf{And with your spirit.}}

\deacon\lectio

\all{\textbf{Glory to you, O Lord.}}

\emph{At the end of the Gospel:}

\deacon\verbumdominib

\all{\textbf{Praise to you, Lord Jesus Christ.}}

\emph{A homily may follow, at which point all sit}

\emph{The Prayer of the Faithful. The reader will conclude each prayer with:}

\reader\exaudi

\emph{To which all respond}

\all{\textbf{Lord graciously hear us.}}

\section*{The Liturgy of the Eucharist}

\emph{The offertorium chant or an appropriate hymn is sung while the altar is prepared for the Liturgy of the Eucharist}

\priest\oratefratres

\all\suscipiat

\emph{The priest sings or says the Prayer over the Offerings, to which all respond:}

\all{\textbf{Amen.}}

\subsection*{The Eucharistic Prayer}

\priest\greeting

\all\etcumc

\priest\sursum

\all\habemus

\priest\gratiasagamus

\all\dignum

\emph{The priest sings or says the Preface, at the end of which all sing or say:}

\all\sanctus

\emph{All kneel}

\priest\mysterium

\all

\mortem

\emph{The Eucharist Prayer continues, concluding with:}

\priest\doxology

\all{\textbf{Amen.}}

\subsection*{The Communion Rite}

\priest\praeceptis

\all{/textbf{Our Father, who art in heaven, Hallowed be Thy name; Thy kingdom come, Thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses, as we forgive those who trespasses against us; and lead us not into temptation, but deliver us from evil.}}

\priest\liberanos

\all{\textbf{For the kingdom, the power and the glory are yours now and forever.}}

\priest\dominejesuchriste

\all{\textbf{Amen.}}

\priest\paxdomini

\all{\textbf{And with your spirit.}}

\deacon\offerte

\all\agnusdei

\priest\ecce

\all\dominenonsum

\emph{While communion is distributed to the faithful, the Communion chant or an appropriate hymn is sung.}

\section*{The Concluding Rites}

\priest\oremus

\emph{The priest sings or says the Prayer after Communion, to which all respond:}

\all{\textbf{Amen.}}

\priest\greeting

\all{\textbf{And with your spirit.}}

\priest\benedicat

\all{\textbf{Amen.}}

\deacon\itemissaest

\all{\textbf{Thanks be to God.}}

\end{document}

